\pkg{DNest4}: Diffusive Nested Sampling in \proglang{C++} and \proglang{Python}

### 2016-05-23 paper/ms.tex
Describing the information, and OPTIONS

\begin{CodeChunk}
\begin{CodeInput}
import dnest4.classic
dnest4.classic.postprocess()
\end{CodeInput}
\end{CodeChunk}
This produces the three diagnostic plots in Figures~\ref{fig:fig1},
\ref{fig:fig2}, and~\ref{fig:fig3}, along with the following output:
\begin{CodeChunk}
\begin{CodeOutput}
log(Z) = -175.528264138 +- 0.0
Information = 15.1944947225 +- 0.0 nats.
Effective sample size = 745.819862383
\end{CodeOutput}
\end{CodeChunk}
These are the natural log of the marginal likelihood, the
information
\begin{align}
\mathcal{H} &= \int p(\theta|D, I)
\ln\left[\frac{p(\theta | D, I)}{p(\theta | I)}\right] \, d\theta
\end{align}
and the number of saved particles with significant posterior weight.
The {\tt postprocess} function also saves a file,
{\tt posterior\_sample.txt}, containing posterior samples (one per row).
The zero-sized error bars on $\ln(Z)$ and $\mathcal{H}$ should be ignored.
These are only relevant if advanced options (not covered in this paper)
are passed to {\tt postprocess}.

@@

The option ``threadSteps'' controls how frequently the separate threads pool
their information about the levels. I usually use 100 or 200. If
(threadSteps) $\times$ (number of threads) is not much smaller than
saveInterval or newLevelInterval, the latter won't be what you expect, because
\dnest~only creates levels or saves particles when the threads are pooling
information.

>>>>

\begin{CodeChunk}
\begin{CodeInput}
import dnest4.classic
dnest4.classic.postprocess()
\end{CodeInput}
\end{CodeChunk}
This produces the three diagnostic plots in Figures~\ref{fig:fig1},
\ref{fig:fig2}, and~\ref{fig:fig3}, along with the following output:
\begin{CodeChunk}
\begin{CodeOutput}
log(Z) = -175.528264138 +- 0.0
Information = 15.1944947225 +- 0.0 nats.
Effective sample size = 745.819862383
\end{CodeOutput}
\end{CodeChunk}
These are the natural log of the marginal likelihood, the
information
\begin{align}
\mathcal{H} &= \int p(\theta|D, I)
\ln\left[\frac{p(\theta | D, I)}{p(\theta | I)}\right] \, d\theta,
\end{align}
which quantifies the degree to which $D$ restricted the
range of possible $\theta$ values,
and the effective sample size,
or number of saved particles with significant posterior weight.
The {\tt postprocess} function also saves a file,
{\tt posterior\_sample.txt}, containing posterior samples (one per row).
The zero-sized error bars on $\ln(Z)$ and $\mathcal{H}$ should be ignored.
These are only relevant if advanced options (not covered in this paper)
are passed to {\tt postprocess}.

@@

The ``thread steps'' parameter controls how frequently separate threads pool
their information about the levels (when running in multi-threaded mode,
see Appendix~\ref{sec:command_line_options}). It should be set to a moderate
value, but should also be a small fraction of the new level interval and the
save interval. 100 is a suggested default value.
